---
title: "Instacart Submission"
author: "Joshua Falter"
date: "May 26, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Instacart Challenge

The goal is to predict which previously purchased products will be in a user's next order.

# Repeat Last Order with only Reordered Products

Trying to recreate the last method located: [here](https://www.kaggle.com/frednavruzov/dumb-and-the-dumber-baselines-plb-0-3276826/notebook)

#Steps
1. Determine which customers need their orders predicted. Using the orders df, use order_id to find user_id for that order.
2. Use order_number and user_id to look up order_number - 1 and get the order_id for it in the orders df.
3. Use order_id to get product_ids of reordered items for each order.
4. Build a df of order_id and product_ids of reordered items.
5. Export to csv as submission



## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
