---
title: "Instacart Submission"
author: "Joshua Falter"
date: "May 26, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Instacart Challenge

The goal is to predict which previously purchased products will be in a user's next order.

# Repeat Last Order with only Reordered Products

Trying to recreate the last method located: [here](https://www.kaggle.com/frednavruzov/dumb-and-the-dumber-baselines-plb-0-3276826/notebook)

# Steps
1. Determine which customers need their orders predicted. Using the orders df, use order_id to find user_id for that order.
2. Use order_number and user_id to look up order_number - 1 and get the order_id for it in the orders df.
3. Use order_id to get product_ids of reordered items for each order.
4. Build a df of order_id and product_ids of reordered items.
5. Export to csv as submission

# Step 1
Just selecting the order_id, user_id, eval_set and order_number from the orders dataframe where eval_set='test'
```{r}
orders_to_predict<-orders[orders$eval_set=='test',c(1:4)]
```
(To check that's its correct we can compare it to sample submissions.csv)

# Step 2
Now we need to look up order_number-1 for each user_id and get the order_id for it
```{r}
order_numbers_to_lookup<-cbind('user_id'= orders_to_predict$user_id,'most_recent_order_number'= orders_to_predict$order_number-1)

colnames(order_numbers_to_lookup)<-c('user_id','order_number')
order_numbers_to_lookup<-as.data.frame(order_numbers_to_lookup)
previous_order_ids<-left_join(order_numbers_to_lookup, orders)
previous_order_ids<-previous_order_ids[c(1,3)]
```
We now have the user_id and order_id of the previous order. Now we just need to get the product_ids for each order from the order_products df.

In Progress


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
